\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[top=0.5in , bottom=0.5in,left=1in, right=1in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{ragged2e}

\raggedright

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }
% DEFINITIONS FOR RESUME

\newcommand{\tab}{\hspacet *{2em}}

\newcommand{\area}[2]{\vspace*{-9pt} \begin{verse}\textbf{#1}   #2 
\end{verse}  }
\newcommand{\lineunder}{\vspace*{-8pt} \\ \hspace*{-18pt} \hrulefill \\}
\newcommand{\header}[1]{{\hspace*{-15pt}\vspace*{6pt} \textsc{#1}} 
\vspace*{-6pt} \lineunder}
\newcommand{\employer}[3]{{ \textbf{#1} \hfill #2\\ \textbf{\emph{#3}}\\  
}}
\newcommand{\employerwithguide}[4]{{ \textbf{#1} \hfill(#2)\\ 
\textbf{\emph{#3}}\\ \emph{#4}  }}
\newcommand{\project}[3]{{ \textbf{#1} (#2)\\ \emph{#3}\\  }}
\newcommand{\projectnoguide}[2]{{ \textbf{#1} (#2)\\  }}
\newcommand{\contact}[2]{
%\vspace*{-8pt} 
\begin{center}
{\LARGE \scshape {#1}}\\
%#2 \lineunder
#2
\end{center}
\vspace*{-8pt}
}
\newcommand{\sbt}{\,\begin{picture}(-1,1)(-1,-3)\circle*{2}\end{picture}\ 
}
\newcommand{\lbt}{\,\begin{picture}(-1,1)(-1,-3)\circle*{3}\end{picture}\ 
}
\newenvironment{achievements}{
    \begin{list}{$\lbt$}{
        \topsep 0pt
        \itemsep 0pt
        \addtolength{\leftmargin}{-0.1in}
    }
}
{
    \vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses}[4]{
 \textbf{#1} \hfill{#2}\\
    #3\\
\vspace*{5pt}
}
\newcommand{\school}[4]{
 \textbf{#1} #2 $\bullet$ #3\\
#4 \\
}

% END RESUME DEFINITIONS

\begin{document}

\pagenumbering{gobble}

\small
\smallskip
\vspace*{-35pt}

% figure out how to link my website

\contact{Nikolai Nekrutenko}
{nan34@cornell.edu $\sbt$ nnekrut.netlify.app $\sbt$ 
github.com/NikolaiTeslovich}
\vspace{2mm}


\header{Education}
\vspace{2mm}
\schoolwithcourses{Cornell University, Ithaca, NY}{Aug 2021 - 
Present}{Undergraduate pursuing a major in Physics with a minor in 
Computer Science}

\schoolwithcourses{Pennsylvania State University, State College, PA}{Jan 
2021 - May 2021}{Non-matriculated student taking Calculus II, General 
Chemistry 1 and 2}
\hfill{}

\header{Coursework}
\vspace{2mm}
\begin{achievements}
\justifying
\item Completed: Honors Mechanics and Special Relativity, Honors 
Electricity and Magnetism, Multi-Variable Calculus, Differential 
Equations, Intro to Computing Using Python  
\item Current Semester: Honors Waves and Thermal Physics, Linear Algebra, 
Objected-Oriented Programming and Data Structures 
\end{achievements}

\header{Experience}
\vspace{2mm}
\schoolwithcourses{Cornell University, Student Researcher}{Mar 2022 - 
Present}
{Member of Professor Valla Fatemi's lab at the department of Applied and 
Engineering Physics. Using QCoDeS, a quantum computer data acquisition 
framework, to run experiments. Interfacing with equipment and sensors over 
VISA by developing drivers in Python. Aiding with the design of 
distillation refrigerators.}

\schoolwithcourses{Cornell Blockchain, Research and Development Team 
Member}{Sep 2021 - Present}
{Worked on establishing a DAO for the club, helped advertise the club to 
attract new applicants, and assisted with club recruitment by interviewing 
several applicants.}

\schoolwithcourses{The Rocket Lab Initiative, Payload Engineer}{Sep 2020 - 
Jun 2021}
{Prototyped a Raspberry Pi sensor payload in a team for a model rocket to 
assess the rocket’s actual performance against that of computer-simulated 
models in a Pennsylvania State University outreach.}

\schoolwithcourses{State High Model Aeronautics Club, President and 
Co-Founder}{Oct 2019 - Jun 2021}{Co-founded a club focused on learning 
about aeronautics through the design, construction, and flight of 
remote-controlled model aircraft. Wrote several grants to accumulate over 
two thousand dollars in funding.}

\schoolwithcourses{Pennsylvania State University, Student Researcher}{Jul 
2019 - Aug 2019}{Member of Professor Slava Rotkin's lab at the Materials 
Research Institute. Developed a Python program in Jupyter Lab to filter 
out background noise from scanning near-field optical microscopy scans.}
\hfill{}

\header{Skills}
\vspace{2mm}
\begin{achievements}
\justifying
\item Fluent in: Russian, French, English
\item Languages: Python, Javascript, Solidity, Shell
\item Programming Tools: git, Jupyter Lab, Pandas, Vega-lite, Observable
\item Website Design: Hugo, Netlify, GitHub Pages, Google Analytics
\item Software: Autodesk Fusion 360, Ultimaker Cura, Blender, Adobe 
Photoshop, Adobe Lightroom, Adobe Premiere Pro, Davinci Resolve, 
OpenRocket
\item Prototyping Skills: Soldering, CNC machine design and operation, CAD 
design and printing using SLA and FDM systems
\item Misc: Arduino, Raspberry Pi, Photography, Cinematography, Drone 
piloting and construction
\end{achievements}

\header{Projects}
\vspace{2mm}
\schoolwithcourses{Developing MinerWrangler}{Nov 2020 - Apr 2021}{Wrote a 
bundle of bash scripts that interacted with the user to automatically 
install and configure Ubuntu Server to work headlessly as a cryptocurrency 
mining server with NVIDIA graphics cards. Documented the installation 
process and usage guide in great detail.}

\schoolwithcourses{Building and Maintaining a Personal Website}{Apr 2020 - 
Present}{Build and regularly update my personal website using Hugo, 
Netlify and Google Analytics with an integrated photo gallery. Made the 
website gain traffic with Google Search Console}

\schoolwithcourses{Raspberry-Pi LED Clock}{Jun 2018 - Aug 2021}{Designed, 
soldered and programmed in python a functional 4-segment Raspberry-Pi 
clock from scratch that syncs with the atomic time servers.}
\hfill{}

\header{Volunteer Experience - get rid of?}
\vspace{2mm}
\schoolwithcourses{A Mountain Wind Martial Arts, Instructor}{Feb 2013 - 
Present}
{First Degree Black Belt in Tang Soo Do, a Korean Martial Art. Instruct 
and help younger students with proper form, technique, and on the 
practical and philosophical applications of the art. Currently designing 
and building a website for the studio.}

\hfill{}
\end{document}
